Naturalness in U(1) extensions of the MSSM

### 2015-01-20 paper/e6ssm-tuning-paper.tex
added to paper plots I want to show for comparing mssm and e6ssm running up to GUT scale.

\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_fixed_at_ms_tuning_plot.png}}\\
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}%%
\caption{Top Panel: Scatter plot of fine tuning vs high scale $M_X$ for benchmark points given in (?).  Left Panel: Individual sensitivites of E6SSM BM plotted against the high scale $M_X$.  Right Panel: Individual sensitivites of MSSM BM plotted against the high scale $M_X$.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_3_points_tuning_plot.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
\\
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_mssm_mixing_small_M3_all_tuning_data.png}}%%
\caption{Top Panel: Scatter plot of fine tuning vs high scale $M_X$ for benchmark points given in (?).  Left Panel: Individual sensitivites of E6SSM BM plotted against the high scale $M_X$.  Right Panel: Individual sensitivites of MSSM BM plotted against the high scale $M_X$.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}
